Seasonality of submesoscale dynamics in the Kuroshio Extension

### 2016-07-10 writeup/rocha_etal.tex
Small fixes

To study seasonal variations in the upper-ocean dynamics, we focus on the northwest
Pacific, in the vicinity of the Kuroshio
Extension, where previous studies have presented strong mesoscale and submesoscale seasonality
\citep{sasaki_etal2014,qiu_etal2014}.
We analyze a sub-domain of the LLC4320 and LLC2160 simulations of about 2000 km$^2$
spanning 155-175$^\circ$E; 25-40$^\circ$N (Figure \ref{fig1}). The stratification
in this mesoscale-rich subtropical region undergoes a vigorous seasonal cycle: wintertime-enhanced
small-scale turbulence de-stratifies the upper ocean, yielding mixed layers
as deep as 300m. In late spring/early summer enhanced solar radiation and mixed-layer
instabilities re-stratify the upper ocean, yielding mixed layers as shallow as 40m.
Fundamentally, the upper-ocean density structure is well-captured by both LLC simulations:
a comparison with Argo climatology shows that both simulations skillfully represent the Kuroshio
Extension stratification and its seasonal variability  (supplemental material).

@@

\begin{figure*}[ht]
  \begin{center}
    \includegraphics[width=.95\textwidth]{figs/fig3.pdf}
 \caption{Seasonal variation of joint probability distributions:  vorticity vs. strain rate (a through d).
          and vorticity vs. Laplacian of sea-surface height (e through h) in April (a, b,
          e, f) and October (c, d, g, h).
          Dashed lines in (a) through (d) represent one dimensional shear flow $\alpha = \pm\zeta$,
          characteristic of fronts. Dashed lines in (e) through
          (h) represent geostrophic flow $\zeta = \frac{g}{f}\nabla_h^2 \eta$.}
 \label{fig3}
 \end{center}
\end{figure*}

@@

\section{Summary and Conclusion}
Our work adds to recent studies that presented modeling \citep{sasaki_etal2014}
and observational \citep{callies_etal2015,buckingham_etal2016} evidence of vigorous seasonality in
submesoscale turbulence. In particular, our main finding is that in global simulations with embedded tides the
near-surface submesoscale inertia-gravity waves in the Kuroshio Extension undergo
a strong seasonal cycle that is out-of-phase with the seasonal cycle of
submesoscale turbulence. We conjecture that the summertime dominance of inertia-gravity waves
 \citep{callies_etal2015} is a consequence both of suppression of submesoscale turbulence and
enhancement of inertia-gravity waves due to re-stratification of
the upper ocean.

>>>>

To study seasonal variations in the upper-ocean dynamics, we focus on the northwest
Pacific, in the vicinity of the Kuroshio
Extension, where previous studies have shown strong mesoscale and submesoscale seasonality
\citep{sasaki_etal2014,qiu_etal2014}.
We analyze a sub-domain of the LLC4320 and LLC2160 simulations of about 2000 km$^2$
spanning 155-175$^\circ$E; 25-40$^\circ$N (Figure \ref{fig1}). The stratification
in this mesoscale-rich subtropical region undergoes a vigorous seasonal cycle: wintertime-enhanced
small-scale turbulence de-stratifies the upper ocean, yielding mixed layers
as deep as 300m. In late spring/early summer enhanced solar radiation and mixed-layer
instabilities re-stratify the upper ocean, yielding mixed layers as shallow as 40m.
Fundamentally, the upper-ocean density structure is well-captured by both LLC simulations:
a comparison with Argo climatology shows that both simulations skillfully represent the Kuroshio
Extension stratification and its seasonal variability  (supplemental material).

@@

\begin{figure*}[ht]
  \begin{center}
    \includegraphics[width=.95\textwidth]{figs/fig3.pdf}
 \caption{Seasonal variation of joint probability distributions:  vorticity vs. strain rate (a through d),
          and vorticity vs. Laplacian of sea-surface height (e through h) in April (a, b,
          e, f) and October (c, d, g, h).
          Dashed lines in (a) through (d) represent one dimensional shear flow $\alpha = \pm\zeta$,
          characteristic of fronts. Dashed lines in (e) through
          (h) represent geostrophic flow $\zeta = \frac{g}{f}\nabla_h^2 \eta$.}
 \label{fig3}
 \end{center}
\end{figure*}

@@

\section{Summary and Conclusion}
Our work adds to recent studies that present modeling \citep{sasaki_etal2014}
and observational \citep{callies_etal2015,buckingham_etal2016} evidence of vigorous seasonality in
submesoscale turbulence. In particular, our main finding is that in global simulations with embedded tides the
near-surface submesoscale inertia-gravity waves in the Kuroshio Extension undergo
a strong seasonal cycle that is out-of-phase with the seasonal cycle of
submesoscale turbulence. We conjecture that the summertime dominance of inertia-gravity waves
 \citep{callies_etal2015} is a consequence both of suppression of submesoscale turbulence and
enhancement of inertia-gravity waves due to re-stratification of
the upper ocean.
